Prehensile Manipulation Planning: Modelling, Algorithms and Implementation

### 2020-10-14 hpp.tex
Add docker directory.

A virtual docker image can be downloaded to run, test and replicate the
examples described in the next sections. After installing docker on a Linux machine, type

\noindent
{\scriptsize\texttt{xhost +\\docker run --rm -it --name hpp \\--volume="/tmp/.X11-unix:/tmp/.X11-unix"\\ gitlab.laas.fr:4567/humanoid-path-planner/hpp-doc/\\ journal2020}}

\noindent
and follow the instructions.

>>>>

A virtual docker image can be downloaded to run, test and replicate the
examples described in the next sections. An archive is provided with this paper
inflate this archive and follow instructions in the README file.
